---
title: "Homework 1"
author: "Dr. Michele Weigle"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

CS 625, Fall 2019

## Setting up your report 

The first thing to do is put in your name in the 
```
author: "Dr. Michele Weigle"
```
line at the top of this file.  You'll do this for every report that you submit.

*Remove this section before submitting your report*

## Setting up R

The command below will load the tidyverse package.  If you have installed R, RStudio, and the tidyverse package, it should display a list of loaded packages and their versions.
```{r}
library(tidyverse)
```

## R Markdown 

1. *Create an ordered bulleted list with at least 3 items*

2. *Write a paragraph that demonstrates the use of italics, bold, bold italics, and code.*

3. *Create an example of a fenced code block.*

4. *Create a level 4 heading*

## R 

#### Data Visualization Exercises

1. *Run ggplot(data = mpg). What do you see?*

2. *How many rows are in mpg? How many columns?*

3. *What does the drv variable describe? Read the help for ?mpg to find out.*

4. *Make a scatterplot of hwy vs cyl.*

5. *What happens if you make a scatterplot of class vs drv? Why is the plot not useful?*


#### Workflow: basics Exercises

1. *Why does this code not work?*

```r
my_variable <- 10
my_varıable
```

2. *Tweak each of the following R commands so that they run correctly:*

```r
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)
filter(diamond, carat > 3)
```

3. *Press Alt + Shift + K. What happens? How can you get to the same place using the menus?*

## Tableau

*Insert your the image of your final bar chart here*

1. *What conclusions can you draw from the chart?*


## Observable and Vega-Lite

#### Intro to Observable notebook
*Insert the URL to your Observable notebook here*

1. *What changes did you make to the notebook?*

2. *What happens when you select a range of items in the scatterplot at the end of the notebook?*

#### Intro to Vega-Lite notebook
*Insert the URL to your Vega-Lite Observable notebook here*

1. *What changes did you make to the notebook?*

*Insert your saved chart image here*

## References

*Insert the list of sites you used as references as an unordered list with named links here.  This is required.*

***Make sure that you Knit your R Markdown into a GitHub-readable Markdown file that is synced with your GitHub repo.***
